
##Loading and preprocessing the data

```{r readingdata, cache=TRUE}
url = "http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(url,destfile="data.zip")
unzip("data.zip")
data<-read.csv("activity.csv")
data$date<-as.Date(data$date)
```

##What is mean total number of steps taken per day?

```{r plot1}
library(plyr)
data1<-ddply(data,.(date), summarize,sum=sum(steps))
hist(data1$sum, col="blue3",
     main="Plot 1. Histogram of number of steps taken",
     xlab="number of steps taken", ylab="frequency")
mean<-mean(data1$sum,na.rm=T)
median<-median(data1$sum,na.rm=T)
```

Average number of steps taken per day is `r as.integer(mean)`.
Median of number of steps taken per day is `r as.integer(median)`.

##Imputing missing values

```{r missing}
sum.na=sum(is.na(data$steps))
pct.na=round(100*sum.na/nrow(data))
```

The number of missing observations is `r sum.na`,
which makes up `r pct.na`% of the observations.

The missing value for will be replaced with mean for each given interval.
```{r imputing}
data$na.replace<-ave(data$steps,data$interval, FUN=function(x) mean(x[!is.na(x)]))
data$steps[is.na(data$steps)]<-data$na.replace[is.na(data$steps)]
```

Revised plot 1 after imputing the missing data
```{r plot1.revised}
data1.revised<-ddply(data,.(date), summarize,sum=sum(steps))
hist(data1.revised$sum, col="blue3",
     main="Plot 1b. Histogram of number of steps taken",
     xlab="number of steps taken", ylab="frequency")
mean<-mean(data1.revised$sum,na.rm=T)
median<-median(data1.revised$sum,na.rm=T)
```
Average number of steps taken per day is `r as.integer(mean)`.
Median of number of steps taken per day is `r as.integer(median)`.


##What is the average daily activity pattern?

```{r plot2}
data2<-ddply(data,.(interval), summarize, avg=mean(steps))
plot(data2$interval, data2$avg, type="l", col="blue4",
     main="Plot 2. Average number of steps taken during each interval",
     xlab="interval", ylab="average number of steps taken")
max<-data2$interval[data2$avg==max(data2$avg)]
```
The interval that contains on average the maximum number of steps 
is interval `r max`

##Are there differences in activity patterns between weekdays and weekends?

``` {r days} 
day<-sapply(data$date, FUN=function(x) 
  {if(weekdays(x, abbreviate=T)=="So"|weekdays(x, abbreviate=T)=="Nd") x<-2
   else x<-1})
data$day<-factor(day,c(1,2),c("weekday","weekend"))
```

``` {r plot3}
library(ggplot2)
data3<-ddply(data,.(day,interval), summarize, avg=mean(steps))
qplot(interval,avg, data=data3,facets=day~.,geom="line",
      xlab="interval", ylab="average number of steps taken")
```


